---
output:
  govdown::govdown_document:
    keep_md: false
    logo_text: "DfE"
    font: "sans-serif"
    title: "Explore education statistics"
    phase: alpha
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(govdown)

file_data <- paste("data_metadata/",your_data_file,'.csv',sep = "")
meta_data <- paste("data_metadata/",your_data_file,'.meta.csv',sep = "")
```
## Underlying data testing{caption=`r Sys.Date()`} 
File tested: `r your_data_file` 

X% of standards met
<br>
```{r files, echo=TRUE, include=FALSE, warning=FALSE, message=FALSE}
dataset <- read_csv(file_data,trim_ws = FALSE)
metadata <- read_csv(meta_data,trim_ws = FALSE)
```
 
```{r files_gui, eval=FALSE}
# Or use this to select your files using a GUI
#dataset <- read_csv(file.choose(),trim_ws = FALSE)
#metadata <- read_csv(file.choose(),trim_ws = FALSE)
```

```{r setup, include=FALSE}
source("setup_functions/all_setup.R")
```
::: {.tabset}

## Data file validation

`r paste(your_data_file,".csv",sep="")`


X% of standards met

:::{.accordion}

## General validation
 **Checking that the compulsory columns are present**
```{r data_comp_col, echo=FALSE,comment=NA}
data_comp_col(dataset)
```

 **Checking for commas in the data file**
```{r comma_check,echo=FALSE,comment=NA}
comma_check(dataset)
```

 **Checking for spaces in the data file variable names**
```{r data_spaces_check,echo=FALSE,comment=NA}
data_spaces_check(dataset)
```

## Time validation
 **Checking that the time_period is either 4 or 6 digits, and if 6 digits that they show  consecutive years**
```{r time_period_check, echo=FALSE,warning=FALSE,comment=NA}
time_period_check(dataset)
```

 **Checking if the time_identifier values are valid**
```{r time_identifier_check,comment=NA,echo=FALSE}
time_identifier_check(dataset)
```

 **Check this list for conceptually different time_identifiers**
```{r time_identifier_mix, echo=FALSE, comment="Time_identifiers: "}
time_identifier_mix(dataset)
```


## Geography validation
 **Checking that the geographic levels are valid**
```{r level_validity_check,echo=FALSE,comment=NA}
level_validity_check(dataset)
```

 **Checking that the correct geography columns are present for the levels in the data file**
```{r geography_levels_present,echo=FALSE,comment=NA}
geography_levels_present(dataset)
```

 **Checking that the correct geography columns are completed for each of the levels in the data file**
```{r geography_level_completed,echo=FALSE,warning=FALSE,comment=NA}
geography_level_completed(dataset)
```

## Filter validation

 **Checking that filters include in the metadata have at least two levels**
```{r filter_levels_check,echo=FALSE,comment=NA}
try(filter_levels_check(dataset,metadata))
```

 **Checking that each filter has a 'Total'**
```{r total_check,echo=FALSE,comment=NA}
try(cat(total_check(dataset,metadata)))
```
 
 **Checking that no observational unit has a 'Total'**
```{r observational_total_check,echo=FALSE,comment=NA}
try(cat(observational_total_check(dataset)))
```
:::

## Metadata validation

`r paste(your_data_file,".meta.csv",sep="")`


X% of standards met

::: {.accordion}
## General validation

 **Checking that the compulsory columns are present**
```{r meta_comp_col,echo=FALSE,comment=NA}
meta_comp_col(metadata)
```

 **Cross checking the columns in the metadata are in the data file**
```{r column_crosscheck,echo=FALSE,warning=FALSE,comment=NA}
column_crosscheck(dataset,metadata)
```

 **Check to catch any variables from the data file that are not in the metadata**
```{r meta_crosscheck,echo=FALSE,warning=FALSE,comment=NA}
meta_crosscheck(dataset,metadata)
```

 **Checking for commas**
```{r meta_comma_check,echo=FALSE,comment=NA}
meta_comma_check(metadata)
```

## Variable and label validation

 **Checking if col_name is completed for every row**
```{r col_name_completed,echo=FALSE,comment=NA}
col_name_completed(metadata)
```

 **Checking for duplicate col_names**
```{r meta_duplicate_check,echo=FALSE,comment=NA}
try(cat(meta_duplicate_check(metadata)))
```

 **Checking for spaces in the values in the col_name column**
```{r col_name_spaces_check,echo=FALSE,comment=NA}
try(cat(col_name_spaces_check(metadata)))
```

 **Checking if any observational units have been erroneously included in the metadata**
```{r comp_col_check_meta,echo=FALSE,warning=FALSE,comment=NA}
comp_col_check_meta(metadata)
```

 **Checking that col_type values are valid**
```{r col_type_check,echo=FALSE,warning=FALSE,comment=NA}
try(cat(col_type_check(metadata)))
```

 **Checking that every row has a label completed**
```{r label_check,echo=FALSE,comment=NA}
try(cat(label_check(metadata)))
```
 
 **Checking that there are no duplicate labels**
```{r duplicate_label_check,echo=FALSE,comment=NA}
try(cat(duplicate_label_check(metadata)))
```

## Filter and indicator validation

 **Checking that no filters have an indicator group**
```{r indicator_group_check,echo=FALSE,comment=NA}
try(cat(indicator_group_check(metadata)))
```

 **Checking that all indicator units are valid values**
```{r indicator_unit_validation,echo=FALSE,comment=NA}
try(cat(indicator_unit_validation(metadata)))
```

 **Checking that no filters have an indicator unit**
```{r indicator_unit_check,echo=FALSE,comment=NA}
indicator_unit_check(metadata)
```

 **Checking that no indicators have a filter hint**
```{r filter_hint_check,echo=FALSE,comment=NA}
try(cat(filter_hint_check(metadata)))
```

 **Checking that no indicators have a filter group**
```{r filter_group_check,echo=FALSE,comment=NA}
try(cat(filter_group_check(metadata)))
```

 **Checking that the number of rows in the metadata is less than the number of columns in the data file**
```{r row_check,echo=FALSE,comment=NA}
try(cat(row_check(dataset,metadata)))
```

 **Checking filter groups are variables in the data file**
```{r filter_group_match,echo=FALSE,comment=NA}
try(cat(filter_group_match(dataset,metadata)))
```

 **Checking that filter and filter group have been entered into the correct columns**
```{r filter_group_levels,echo=FALSE,comment=NA}
try(cat(filter_group_levels(dataset,metadata)))
```


:::
:::

:::{.details summary="Further information"}
:::{.warning}
 For further information, or if you have any questions about this report contact cameron.race@education.gov.uk.
:::
:::